Naturalness and Long-Lived Beyond the Standard Model Particles

### 2017-07-30 tex/draft.tex
Add most figures

\usepackage[final]{fixme}
\fxsetup{layout=footnote}
\usepackage[left]{lineno}
\usepackage[demo]{graphicx}
\usepackage{amsmath,amsthm,amssymb,mathtools,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
\usepackage{fullpage}

@@

    SM parameters, such as particle masses\fxnote{what else is corrected. How?}, are corrected by interactions with virtual particles through loop diagrams. Fig.~\ref{loop_diagrams}, for example, shows the potential corrections to the Higgs and electron masses. Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid. The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{check. be able to work out example} on $\Lambda$. The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.

    \noindent \begin{figure}[htbp] \begin{center}
    \includegraphics[width=0.8\textwidth]{images/loop_diagrams}
    \caption{Caption!\fxnote{cite something}}
    \label{loop_diagrams}
    \end{center} \end{figure}

@@

    \noindent \begin{figure}[htbp] \begin{center}
    \includegraphics[width=0.8\textwidth]{images/exact_susy_correction}
    \caption{Caption!\fxnote{cite something}}
    \label{exact_susy_correction}
    \end{center} \end{figure}

@@

    \noindent \begin{figure}[htbp] \begin{center}
    \includegraphics[width=0.8\textwidth]{images/rp_and_rpv_diagrams}
        \caption{R-parity and RPV diagrams}
    \label{rp_and_rpv_diagrams}
    \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/cms}
            \caption{CMS}
        \label{cms}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/jamie_cartoon}
            \caption{Diagram of several LLP spectra}
        \label{jamie_cartoon}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/displaced_process_diagram}
        \caption{Process.}
        \label{displaced_process}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/material_map}
        \caption{Map of material dense regions of the ATLAS detector.\fxnote{cite analysis}}
        \label{material_map}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/displaced_limit}
        \caption{Limit.}
        \label{displaced_limit}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/disappearing_processes}
        \caption{Processes.}
        \label{disappearing_processes}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/disappearing_limits}
        \caption{Limits.}
        \label{disappearing_limits}
        \end{center} \end{figure}

@@

        This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps). Long-lived gluinos can appear in models such as split\fxnote{capitalize?} SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light. After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs, as shown in Fig.~\ref{stopped_process}. The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/stopped_process}
            \caption{Long-lived gluino proces.\fxnote{cite analysis}}
        \label{stopped_process}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/stopped_muon_differentiation}
            \caption{Cosmic muon rejection with MS.\fxnote{cite analysis}}
        \label{stopped_muon_differentiation}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/stopped_limits}
            \caption{Limits.\fxnote{cite analysis}}
        \label{stopped_limits}
        \end{center} \end{figure}

    \subsection{Heavy Stable Charged Particles}
        \fxnote{cite CMS EXO7-010}
        \fxnote{Specify dataset}
        \fxnote{nice dE/dx plot (fig 1)}
        Particles that live for more than a couple ns\fxnote{how do I typeset standalone units?} \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying. If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP). HSCPs are characterterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview. Probably better explained here than there}. Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}.

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/hscp_dedx}
            \caption{Ionization energy loss.\fxnote{cite analysis}}
        \label{hscp_dedx}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.8\textwidth]{images/hscp_limits}
            \caption{Limits.\fxnote{cite analysis}}
        \label{hscp_limits}
        \end{center} \end{figure}

>>>>

\usepackage[final]{graphicx}
\usepackage[final]{fixme}
\fxsetup{layout=footnote}
\usepackage[left]{lineno}
\usepackage{tikz-feynman}
\usepackage{amsmath,amsthm,amssymb,mathtools,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
\usepackage{fullpage}

@@

    SM parameters, such as particle masses\fxnote{what else is corrected. How?}, are corrected by interactions with virtual particles through loop diagrams. Fig.~\ref{loop_diagrams}, for example, shows corrections to the Higgs and electron masses. Because the Higgs is a fundamental scalar, its corrections depend quadratically on the cutoff scale, $\Lambda$, which is the largest energy scale for which the SM is valid. The fermions and gauge bosons, on the other hand, only depend logarithmically\fxnote{check. be able to work out example} on $\Lambda$. The next section explores the concept of naturalness, a major motivating principle for beyond the standard model (BSM) physics that is directly tied to the relationship between the bare Higgs mass and the terms that correct it.

    \noindent \begin{figure}[htbp] \begin{center}
        \feynmandiagram [layered layout, horizontal=b to c] {
            a -- [scalar] b,
            b -- [fermion, half left] c,
            c -- [fermion, half left] b,
            c -- [scalar] d,
        };
        \qquad
        \feynmandiagram [layered layout, horizontal=b to c] {
            a -- [fermion] b,
            b -- [fermion] c,
            b -- [photon, half left] c,
            c -- [opacity=0.0, half left] b,
            c -- [fermion] d,
        };
        \caption{Higgs mass (left) corrected by fermion loop and fermion mass (right) corrected by photon loop.\fxnote{cite tikz-feyman}}
        \label{loop_diagrams}
    \end{center} \end{figure}

@@

    \noindent \begin{figure}[htbp] \begin{center}
        \feynmandiagram [inline=(d.base), layered layout, horizontal=b to c] {
        a -- [scalar] b,
        b -- [fermion, half left] c,
        c -- [fermion, half left] b,
        c -- [scalar] d,
    };
    \quad + \quad
    \feynmandiagram [baseline={(current bounding box.center)}, layered layout, horizontal=b to c] {
        a -- [scalar] b,
        b -- [charged scalar, half left] c,
        c -- [charged scalar, half left] b,
        c -- [scalar] d,
    };
    \quad = \quad 0 \quad
    \caption{Caption!\fxnote{cite something}}
    \label{exact_susy_correction}
    \end{center} \end{figure}

@@

    \noindent \begin{figure}[htbp] \begin{center}
    \includegraphics[width=0.3\textwidth]{images/rp_and_rpv_diagrams}
        \caption{R-parity and RPV diagrams}
    \label{rp_and_rpv_diagrams}
    \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.7\textwidth]{images/cms}
            \caption{CMS}
        \label{cms}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.7\textwidth]{images/jamie_cartoon}
            \caption{Diagram of several LLP spectra}
        \label{jamie_cartoon}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \feynmandiagram [layered layout, horizontal=a to b] {
            a -- [plain, gluon] b,
            b -- [anti charged scalar] c,
            b -- [fermion] d,
            c -- [anti fermion] e,
            c -- [plain, boson] f,
        };
        \caption{Process.}
        \label{displaced_process}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.6\textwidth]{images/material_map}
        \caption{Map of material dense regions of the ATLAS detector.\fxnote{cite analysis}}
        \label{material_map}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/displaced_cross_section_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/displaced_mass_limit}
        \end{center} \end{subfigure}
        \caption{Limit.}
        \label{displaced_limit}
        \end{center} \end{figure}

@@

        \fxnote{ugh, this is too hard. just steal diagram from paper or make in jaxodraw. Maybe even use simulated event instead, but make sure I can draw these if asked?}  
        \noindent \begin{figure}[htbp] \begin{center}
        \feynmandiagram [layered layout] {
            i1 -- [plain] a [blob],
            i2 -- [plain] a,
            a -- [plain, boson] b [blob],
            a -- [plain] f1,
            a -- [plain, boson] f2,
            b -- [plain, boson] f3,
            b -- [scalar] f4,
        };
        \caption{Processes.}
        \label{disappearing_processes}
        \end{center} \end{figure}

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_ew_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_strong_200ps_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.3\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_strong_1ns_limit}
        \end{center} \end{subfigure}
        \caption{Limits.}
        \label{disappearing_limits}
        \end{center} \end{figure}

@@

        This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps). Long-lived gluinos can appear in models such as split\fxnote{capitalize?} SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light. After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs. This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}. The gluino decay is supressed by the large squark mass, which leads to its appreciable lifetime.

@@

        \fxnote{check if tof, beta, or bx is better} 
        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=\textwidth]{images/stopped_reject_cosmic_tof}
        \caption{Cosmic muon rejection with MS.\fxnote{cite analysis}}
        \label{stopped_muon_differentiation}
        \end{center} \end{figure}

@@

        \fxnote{ok to skip mchamp? Be able to explain why} 
        \noindent \begin{figure}[htbp] \begin{center}
        \begin{subfigure}[htbp]{0.5\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/stopped_limit_gluino_cross_section}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/stopped_limit_gluino_mass}
        \end{center} \end{subfigure}
        \caption{Limits.\fxnote{cite analysis}}
        \label{stopped_limits}
        \end{center} \end{figure}

    \subsection{Heavy Stable Charged Particles}
        \fxnote{cite CMS EXO-15-010}
        \fxnote{Specify dataset}
        \fxnote{nice dE/dx plot (fig 1)}
        Particles that live for more than a couple ns\fxnote{how do I typeset standalone units?} \fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying. If such a particle is also sufficiently massive, it can be catigorized as a heavy stable charged particle (HSCP). HSCPs are characterterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview. Probably better explained here than there}. Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}.

        \noindent \begin{figure}[htbp] \begin{center}
        \includegraphics[width=0.5\textwidth]{images/hscp_dedx}
            \caption{Ionization energy loss.\fxnote{cite analysis}}
        \label{hscp_dedx}
        \end{center} \end{figure}

@@

        \fxnote{I show seperate trk, trk+tof limits but never explain that in text} 
        \noindent \begin{figure}[htbp] \begin{center}
        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/hscp_limit_tracker_only}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.45\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/hscp_limit_tracker_tof}
        \end{center} \end{subfigure}
        \caption{Limits.\fxnote{cite analysis}}
        \label{hscp_limits}
        \end{center} \end{figure}
